### 2017-02-24 case/arf.tex
\it{DATA}

\sloppy{%
  Fig.~\ref{fig:arf_sm} shows the state machine $S$ for the packet trace
  collected at sender (DUT), where $DATA_i^r$ denotes a data packet
  with sequence number $i$ and bit rate $r$, $DATA_i^{r\prime}$ is a retransmission packet
  and $Ack$ is the acknowledgment packet. The \texttt{pkg\_succ} function is
  shown in Algorithm~\ref{alg:pkt_succ}.
}

>>>>

\sloppy{%
  Fig.~\ref{fig:arf_sm} shows the state machine $S$ for the packet trace
  collected at sender (DUT), where $\it{DATA}_i^r$ denotes a data packet
  with sequence number $i$ and bit rate $r$, $\it{DATA}_i^{r\prime}$ is a retransmission packet
  and $Ack$ is the acknowledgment packet. The \texttt{pkg\_succ} function is
  shown in Algorithm~\ref{alg:pkt_succ}.
}

### 2017-02-24 case/tx.tex
\it{DATA}

A na\"ive way to calculate the Jaccard distance of two traces is to use the hash
of the $(time, packet)$ pair for set intersection and union operation.  However,
it does not work for mutation trace which contains fabricated packets with no
actual payload.  Therefore, we use a protocol specific canonical representation
of packets when calculating the distance.  In particular, the string
\texttt{r\_DATA\_i\_t} represents the $t^{th}$ transmission of a data packet
with sequence number $i$, and $r$ represents the round of sequence numbers as it
wraps after 4096.  And similarly \texttt{r\_Ack\_i\_t} is the corresponding
acknowledgment packet.

>>>>

A na\"ive way to calculate the Jaccard distance of two traces is to use the hash
of the $(time, packet)$ pair for set intersection and union operation.  However,
it does not work for mutation trace which contains fabricated packets with no
actual payload.  Therefore, we use a protocol specific canonical representation
of packets when calculating the distance.  In particular, the string
\texttt{r\_\it{DATA}\_i\_t} represents the $t^{th}$ transmission of a data packet
with sequence number $i$, and $r$ represents the round of sequence numbers as it
wraps after 4096.  And similarly \texttt{r\_Ack\_i\_t} is the corresponding
acknowledgment packet.

### 2017-02-24 framework/heuristic.tex
\it{DATA}

Consider the 802.11 data transmission protocol and the example trace snippet
shown in Figure~\ref{fig:loss}, the packet loss ratios are:
\begin{align*}
  Pr_{ds} &= \frac{\parallel\{DATA'_0\}\parallel}{\parallel\{DATA_0, DATA'_0\}\parallel} = 0.5\\
  Pr_{es} &= \frac{\parallel\emptyset\parallel}{\parallel\{Ack, Ack\}\parallel} = 0\\
  Pr_{ed} &= \frac{\parallel\{Ack\}\parallel}{\parallel\{Ack, Ack\}\parallel\times (1-Pr_{es})} = 0.5
\end{align*}

>>>>

Consider the 802.11 data transmission protocol and the example trace snippet
shown in Figure~\ref{fig:loss}, the packet loss ratios are:
\begin{align*}
  Pr_{ds} &= \frac{\parallel\{\it{DATA}'_0\}\parallel}{\parallel\{\it{DATA}_0, \it{DATA}'_0\}\parallel} = 0.5\\
  Pr_{es} &= \frac{\parallel\emptyset\parallel}{\parallel\{Ack, Ack\}\parallel} = 0\\
  Pr_{ed} &= \frac{\parallel\{Ack\}\parallel}{\parallel\{Ack, Ack\}\parallel\times (1-Pr_{es})} = 0.5
\end{align*}

### 2017-02-24 motivation.tex
title page format
\it{DATA}

\begin{figure}[H]
  \vspace*{-3mm}
  \centering
  \includegraphics[width=0.6\textwidth]{./figures/dot11_tx_ta.pdf}
  \caption{\textbf{Monitor State Machine for 802.11 Transmitter.}}
  \label{fig:dot11_tx_ta}
  \vspace*{-3mm}
\end{figure}

To better understand the incompleteness of sniffer trace, consider the IEEE
802.11 (also known as \wifi{}) transmitter (DUT) state machine shown in
Fig.~\ref{fig:dot11_tx_ta}. After the DUT sends $DATA_i$---a data packet with
sequence number $i$ ($s_0\rightarrow s_1)$, it starts a timer and waits for the
acknowledgment packet---$Ack$. The DUT either receives $Ack$ within time $T_o$
($s_1\rightarrow s_0$), or it sends $DATA'_i$---retransmission of $DATA_i$
($s_1\rightarrow s_2$). Similarly, the DUT either receives the $Ack$ within $T_o$
($s_2\rightarrow s_0$) or aborts transmission and moves on to next
packet\footnote{To represent the state machine succinctly, our example assumes
that the DUT retries at most once.} ($s_2\rightarrow s_1$).

@@

Consider a correct packet exchange sequence shown in
Fig.~\ref{fig:sniffer_in_middle}. The DUT first sends $DATA_0$.  Suppose the
receiver receives $DATA_0$ and sends the $Ack$ which the DUT does not receive.
Eventually the DUT's timer fires and it sends $DATA'_0$.  This time the
$DATA'_0$ reaches receiver and the DUT also receives the $Ack$.

Now consider two possible traces that could have been overheard by a sniffer shown
in Fig.~\ref{fig:sniffer_in_middle}.
In first sniffer trace $Tr_1$ where the sniffer
\textit{overhears} the first $Ack$ packet, a validation \textit{uncertainty}
arises when the sniffer sees the $DATA'_0$: was the previous $Ack$ missed by the
DUT or is there a bug in DUT which causes it to retransmit even after receiving
the $Ack$?

Similarly, consider the second possible sniffer trace $Tr_2$
where both the $DATA'_0$ and $Ack$ packets were missed by the sniffer. During
this period of time, it appears the DUT neither receives $Ack$ for $DATA_0$ nor
sends $DATA'_0$. Again, without any additional information it is impossible to
disambiguate between the sniffer missing certain packets and a bug in DUT's
retransmission logic.

>>>>

\begin{figure}[t!]
  \centering
  \includegraphics[width=0.6\textwidth]{./figures/dot11_tx_ta.pdf}
  \caption{\textbf{Monitor State Machine for 802.11 Transmitter.}}
  \label{fig:dot11_tx_ta}
\end{figure}

To better understand the incompleteness of sniffer trace, consider the IEEE
802.11 (also known as \wifi{}) transmitter (DUT) state machine shown in
Fig.~\ref{fig:dot11_tx_ta}. After the DUT sends $\it{DATA}_i$---a data packet with
sequence number $i$ ($s_0\rightarrow s_1)$, it starts a timer and waits for the
acknowledgment packet---$Ack$. The DUT either receives $Ack$ within time $T_o$
($s_1\rightarrow s_0$), or it sends $\it{DATA}'_i$---retransmission of $\it{DATA}_i$
($s_1\rightarrow s_2$). Similarly, the DUT either receives the $Ack$ within $T_o$
($s_2\rightarrow s_0$) or aborts transmission and moves on to next
packet\footnote{To represent the state machine succinctly, our example assumes
that the DUT retries at most once.} ($s_2\rightarrow s_1$).

@@

Consider a correct packet exchange sequence shown in
Fig.~\ref{fig:sniffer_in_middle}. The DUT first sends $\it{DATA}_0$.  Suppose the
receiver receives $\it{DATA}_0$ and sends the $Ack$ which the DUT does not receive.
Eventually the DUT's timer fires and it sends $\it{DATA}'_0$.  This time the
$\it{DATA}'_0$ reaches receiver and the DUT also receives the $Ack$.

Now consider two possible traces that could have been overheard by a sniffer shown
in Fig.~\ref{fig:sniffer_in_middle}.
In first sniffer trace $Tr_1$ where the sniffer
\textit{overhears} the first $Ack$ packet, a validation \textit{uncertainty}
arises when the sniffer sees the $\it{DATA}'_0$: was the previous $Ack$ missed by the
DUT or is there a bug in DUT which causes it to retransmit even after receiving
the $Ack$?

Similarly, consider the second possible sniffer trace $Tr_2$
where both the $\it{DATA}'_0$ and $Ack$ packets were missed by the sniffer. During
this period of time, it appears the DUT neither receives $Ack$ for $\it{DATA}_0$ nor
sends $\it{DATA}'_0$. Again, without any additional information it is impossible to
disambiguate between the sniffer missing certain packets and a bug in DUT's
retransmission logic.
